Estimating duration in the presence of misclassification

### 2024-02-14 transmission-appendix-INLA.tex
start working through to do list in ch 7

>>>>

\chapter{INLA} \label{transmission:sec:INLA}

INLA (Integrated Nested Laplace Approximation) is a method for approximate Bayesian inference.
It was introduced by \textcite{rueINLA}.
This appendix is based on that paper, as well as the seminar \textcite{rueINLAseminar} and the tutorial paper \textcite{martinoINLAtutorial}.

\section{Inference procedure} \label{transmission:sec:INLA:inference}

\section{Drawing from the posterior} \label{transmission:sec:INLA:posterior}

\section{Default priors} \label{transmission:sec:INLA:priors}
